---
title: "Parameter_tuning14-26"
author: "RuiWang"
date: '2022-09-14'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# NO.14 Illinois
order=c(2,1,2),seasonal=c(1,0,2))AICc=93.64 RMSE 0.6938496
# NO.15 Indiana
order=c(1,1,1),seasonal=c(0,1,1))AICc=150.93 RMSE 0.4969712
# NO.16 Iowa
order=c(1,1,2),seasonal=c(1,1,1)) AICc=-177.73 RMSE 0.5313282
# NO.17 Kansas
order=c(3,1,4),seasonal=c(0,1,2))AICc=-202.92 RMSE 0.3559289
# NO.18 Kentucky
order=c(3,0,1),seasonal=c(1,1,1)) AICc=40.98 RMSE 0.7142507
# NO.19 Kentucky
order=c(5,1,2),seasonal=c(0,1,1))AICc=178.62 RMSE 0.5966853
# NO.20 Maine
order=c(3,1,3),seasonal=c(1,1,3))AICc=20.93 RMSE 0.3488586
# NO.21 Maryland
order=c(2,1,1),seasonal=c(3,1,1))AICc=-155.04 RMSE0.6156309
# NO.22 Massachusetts
order=c(1,1,2),seasonal=c(0,1,1))AICc=-413.85 RMSE 0.4157668
# NO.23 Michigan
order=c(2,0,1),seasonal=c(0,1,1))AICc=294.23 RMSE 0.9963709
# NO.24 Minnesota
order=c(3,0,2),seasonal=c(3,1,1))AICc=-144.05 RMSE 0.6711534
# NO.25 Mississippi
order=c(3,0,2),seasonal=c(3,1,1))AICc=385.84 RMSE 0.6710053
# NO.26 Missouri
order=c(3,0,1),seasonal=c(0,1,1))AICc=-49.16 RMSE 0.7054886
```{r}
library(forecast)
library(tseries)
library(Metrics)
usadata = read.csv(file = 'F:/UNIMELB/Graduate/DSProject/Data-scence-project/data/usa_unemployment_nsa.csv')
labour = read.csv(file = 'F:/UNIMELB/Graduate/DSProject/Data-scence-project/data/labour_backup.csv')
percentage = read.csv(file = 'F:/UNIMELB/Graduate/DSProject/Data-scence-project/data/rate.csv')
```
# NO.14 Illinois
order=c(2,1,2),seasonal=c(1,0,2))AICc=93.64 RMSE 0.6938496
```{r}
usadata[14,1]
state14 = c(usadata[14,])
state14 = state14[2:length(state14)]
state_raw = as.vector(unlist(state14))
ts_state_data=ts(state_raw,start=c(1976, 1), end=c(2018, 12), frequency=12)

# p-value = 0.005 < 0.05
autoresult = auto.arima(ts_state_data,seasonal = TRUE)
checkresiduals(autoresult)#p_v=2.2e-16

#record RMSE
fore = forecast(autoresult,h=24)
tnew=state_raw[(length(state_raw)-51):(length(state_raw)-28)]
tnewnew = t(t(as.vector(fore$mean[1:length(fore$mean)])))

rmse(tnew, tnewnew)#0.55195

# check acf and pacf plot
acf(ts_state_data)
pacf(ts_state_data)
# p-value >0.05 non-stationary
adf.test(ts_state_data)

# difference ts , d = 1
d = diff(ts_state_data, differences=1)
plot.ts(d)

#get p and q from plots
acf(d)
pacf(d)
adf.test(d)
ts_state_data %>% diff(lag=12) %>% diff() %>% ggtsdisplay()

#try orders
t=Arima(ts_state_data,order=c(2,1,2),seasonal=c(1,0,2))
t %>% residuals() %>% ggtsdisplay()
checkresiduals(t,plot = FALSE)
#p-value > 0.05 means significant 

#check AICc
t

#check RMSE
fore = forecast(t,h=24)

tnew=state_raw[(length(state_raw)-51):(length(state_raw)-28)]
tnewnew = t(t(as.vector(fore$mean[1:length(fore$mean)])))

rmse(tnew, tnewnew)
```
# NO.15 Indiana
order=c(1,1,1),seasonal=c(0,1,1))AICc=150.93 RMSE 0.4969712
```{r}
usadata[15,1]
state15 = c(usadata[15,])
state15 = state15[2:length(state15)]
state_raw = as.vector(unlist(state15))
ts_state_data=ts(state_raw,start=c(1976, 1), end=c(2018, 12), frequency=12)

# p-value = 0.005 < 0.05
autoresult = auto.arima(ts_state_data,seasonal = TRUE)
checkresiduals(autoresult)#p_v=

#record RMSE
fore = forecast(autoresult,h=24)
tnew=state_raw[(length(state_raw)-51):(length(state_raw)-28)]
tnewnew = t(t(as.vector(fore$mean[1:length(fore$mean)])))

rmse(tnew, tnewnew)#0.55195

# check acf and pacf plot
acf(ts_state_data)
pacf(ts_state_data)
# p-value >0.05 non-stationary
adf.test(ts_state_data)

# difference ts , d = 1
d = diff(ts_state_data, differences=1)
plot.ts(d)

#get p and q from plots
acf(d)
pacf(d)
adf.test(d)
ts_state_data %>% diff(lag=12) %>% diff() %>% ggtsdisplay()

#try orders
t=Arima(ts_state_data,order=c(1,1,1),seasonal=c(0,1,1))
t %>% residuals() %>% ggtsdisplay()
checkresiduals(t,plot = FALSE)
#p-value > 0.05 means significant 

#check AICc
t

#check RMSE
fore = forecast(t,h=24)

tnew=state_raw[(length(state_raw)-51):(length(state_raw)-28)]
tnewnew = t(t(as.vector(fore$mean[1:length(fore$mean)])))

rmse(tnew, tnewnew)
```
# NO.16 Iowa
order=c(1,1,2),seasonal=c(1,1,1)) AICc=-177.73 RMSE 0.5313282

```{r}
usadata[16,1]
state16 = c(usadata[16,])
state16 = state16[2:length(state16)]
state_raw = as.vector(unlist(state16))
ts_state_data=ts(state_raw,start=c(1976, 1), end=c(2018, 12), frequency=12)

# p-value = 0.005 < 0.05
autoresult = auto.arima(ts_state_data,seasonal = TRUE)
checkresiduals(autoresult)#p_v=

#record RMSE
fore = forecast(autoresult,h=24)
tnew=state_raw[(length(state_raw)-51):(length(state_raw)-28)]
tnewnew = t(t(as.vector(fore$mean[1:length(fore$mean)])))

rmse(tnew, tnewnew)#0.55195

# check acf and pacf plot
acf(ts_state_data)
pacf(ts_state_data)
# p-value >0.05 non-stationary
adf.test(ts_state_data)

# difference ts , d = 1
d = diff(ts_state_data, differences=1)
plot.ts(d)

#get p and q from plots
acf(d)
pacf(d)
adf.test(d)
ts_state_data %>% diff(lag=12) %>% diff() %>% ggtsdisplay()

#try orders
t=Arima(ts_state_data,order=c(1,1,1),seasonal=c(0,1,1))
t %>% residuals() %>% ggtsdisplay()
checkresiduals(t,plot = FALSE)
#p-value > 0.05 means significant 

#check AICc
t

#check RMSE
fore = forecast(t,h=24)

tnew=state_raw[(length(state_raw)-51):(length(state_raw)-28)]
tnewnew = t(t(as.vector(fore$mean[1:length(fore$mean)])))

rmse(tnew, tnewnew)
```
# NO.17 Kansas
order=c(3,1,4),seasonal=c(0,1,2))AICc=-202.92 RMSE 0.3559289

```{r}
usadata[17,1]
state = c(usadata[17,])
state = state[2:length(state)]
state_raw = as.vector(unlist(state))
ts_state_data=ts(state_raw,start=c(1976, 1), end=c(2018, 12), frequency=12)

# p-value = 0.005 < 0.05
autoresult = auto.arima(ts_state_data,seasonal = TRUE)
checkresiduals(autoresult)#p_v=

#record RMSE
fore = forecast(autoresult,h=24)
tnew=state_raw[(length(state_raw)-51):(length(state_raw)-28)]
tnewnew = t(t(as.vector(fore$mean[1:length(fore$mean)])))

rmse(tnew, tnewnew)#0.55195

# check acf and pacf plot
acf(ts_state_data)
pacf(ts_state_data)
# p-value >0.05 non-stationary
adf.test(ts_state_data)

# difference ts , d = 1
d = diff(ts_state_data, differences=1)
plot.ts(d)

#get p and q from plots
acf(d)
pacf(d)
adf.test(d)
ts_state_data %>% diff(lag=12) %>% diff() %>% ggtsdisplay()

#try orders
t=Arima(ts_state_data,order=c(1,1,1),seasonal=c(0,1,1))
t %>% residuals() %>% ggtsdisplay()
checkresiduals(t,plot = FALSE)
#p-value > 0.05 means significant 

#check AICc
t

#check RMSE
fore = forecast(t,h=24)

tnew=state_raw[(length(state_raw)-51):(length(state_raw)-28)]
tnewnew = t(t(as.vector(fore$mean[1:length(fore$mean)])))

rmse(tnew, tnewnew)
```
# NO.18 Kentucky
order=c(3,0,1),seasonal=c(1,1,1)) AICc=40.98 RMSE 0.7142507

```{r}
usadata[18,1]
state = c(usadata[18,])
state = state[2:length(state)]
state_raw = as.vector(unlist(state))
ts_state_data=ts(state_raw,start=c(1976, 1), end=c(2018, 12), frequency=12)

# p-value = 0.005 < 0.05
autoresult = auto.arima(ts_state_data,seasonal = TRUE)
checkresiduals(autoresult)#p_v=

#record RMSE
fore = forecast(autoresult,h=24)
tnew=state_raw[(length(state_raw)-51):(length(state_raw)-28)]
tnewnew = t(t(as.vector(fore$mean[1:length(fore$mean)])))

rmse(tnew, tnewnew)#0.55195

# check acf and pacf plot
acf(ts_state_data)
pacf(ts_state_data)
# p-value >0.05 non-stationary
adf.test(ts_state_data)

# difference ts , d = 1
d = diff(ts_state_data, differences=1)
plot.ts(d)

#get p and q from plots
acf(d)
pacf(d)
adf.test(d)
ts_state_data %>% diff(lag=12) %>% diff() %>% ggtsdisplay()

#try orders
t=Arima(ts_state_data,order=c(1,1,1),seasonal=c(0,1,1))
t %>% residuals() %>% ggtsdisplay()
checkresiduals(t,plot = FALSE)
#p-value > 0.05 means significant 

#check AICc
t

#check RMSE
fore = forecast(t,h=24)

tnew=state_raw[(length(state_raw)-51):(length(state_raw)-28)]
tnewnew = t(t(as.vector(fore$mean[1:length(fore$mean)])))

rmse(tnew, tnewnew)
```
# NO.19 Kentucky
order=c(5,1,2),seasonal=c(0,1,1))AICc=178.62 RMSE 0.5966853

```{r}
usadata[19,1]
state = c(usadata[19,])
state = state[2:length(state)]
state_raw = as.vector(unlist(state))
ts_state_data=ts(state_raw,start=c(1976, 1), end=c(2018, 12), frequency=12)

# p-value = 0.005 < 0.05
autoresult = auto.arima(ts_state_data,seasonal = TRUE)
checkresiduals(autoresult)#p_v=

#record RMSE
fore = forecast(autoresult,h=24)
tnew=state_raw[(length(state_raw)-51):(length(state_raw)-28)]
tnewnew = t(t(as.vector(fore$mean[1:length(fore$mean)])))

rmse(tnew, tnewnew)#0.55195

# check acf and pacf plot
acf(ts_state_data)
pacf(ts_state_data)
# p-value >0.05 non-stationary
adf.test(ts_state_data)

# difference ts , d = 1
d = diff(ts_state_data, differences=1)
plot.ts(d)

#get p and q from plots
acf(d)
pacf(d)
adf.test(d)
ts_state_data %>% diff(lag=12) %>% diff() %>% ggtsdisplay()

#try orders
t=Arima(ts_state_data,order=c(7,1,3),seasonal=c(1,1,1))
t %>% residuals() %>% ggtsdisplay()
checkresiduals(t,plot = FALSE)
#p-value > 0.05 means significant 

#check AICc
t

#check RMSE
fore = forecast(t,h=24)

tnew=state_raw[(length(state_raw)-51):(length(state_raw)-28)]
tnewnew = t(t(as.vector(fore$mean[1:length(fore$mean)])))

rmse(tnew, tnewnew)
```
# NO.20 Maine
order=c(3,1,3),seasonal=c(1,1,3))AICc=20.93 RMSE 0.3488586

```{r}
usadata[20,1]
state = c(usadata[20,])
state = state[2:length(state)]
state_raw = as.vector(unlist(state))
ts_state_data=ts(state_raw,start=c(1976, 1), end=c(2018, 12), frequency=12)

# p-value = 0.005 < 0.05
autoresult = auto.arima(ts_state_data,seasonal = TRUE)
checkresiduals(autoresult)#p_v=

#record RMSE
fore = forecast(autoresult,h=24)
tnew=state_raw[(length(state_raw)-51):(length(state_raw)-28)]
tnewnew = t(t(as.vector(fore$mean[1:length(fore$mean)])))

rmse(tnew, tnewnew)#0.55195

# check acf and pacf plot
acf(ts_state_data)
pacf(ts_state_data)
# p-value >0.05 non-stationary
adf.test(ts_state_data)

# difference ts , d = 1
d = diff(ts_state_data, differences=1)
plot.ts(d)

#get p and q from plots
acf(d)
pacf(d)
adf.test(d)
ts_state_data %>% diff(lag=12) %>% diff() %>% ggtsdisplay()

#try orders
t=Arima(ts_state_data,order=c(3,1,3),seasonal=c(1,1,3))
t %>% residuals() %>% ggtsdisplay()
checkresiduals(t,plot = FALSE)
#p-value > 0.05 means significant 

#check AICc
t

#check RMSE
fore = forecast(t,h=24)

tnew=state_raw[(length(state_raw)-51):(length(state_raw)-28)]
tnewnew = t(t(as.vector(fore$mean[1:length(fore$mean)])))

rmse(tnew, tnewnew)
```
# NO.21 Maryland
order=c(2,1,1),seasonal=c(3,1,1))AICc=-155.04 RMSE0.6156309

```{r}
usadata[21,1]
state = c(usadata[21,])
state = state[2:length(state)]
state_raw = as.vector(unlist(state))
ts_state_data=ts(state_raw,start=c(1976, 1), end=c(2018, 12), frequency=12)

# p-value = 0.005 < 0.05
autoresult = auto.arima(ts_state_data,seasonal = TRUE)
checkresiduals(autoresult)#p_v=

#record RMSE
fore = forecast(autoresult,h=24)
tnew=state_raw[(length(state_raw)-51):(length(state_raw)-28)]
tnewnew = t(t(as.vector(fore$mean[1:length(fore$mean)])))

rmse(tnew, tnewnew)#0.55195

# check acf and pacf plot
acf(ts_state_data)
pacf(ts_state_data)
# p-value >0.05 non-stationary
adf.test(ts_state_data)

# difference ts , d = 1
d = diff(ts_state_data, differences=1)
plot.ts(d)

#get p and q from plots
acf(d)
pacf(d)
adf.test(d)
ts_state_data %>% diff(lag=12) %>% diff() %>% ggtsdisplay()

#try orders
t=Arima(ts_state_data,order=c(2,1,1),seasonal=c(3,1,1))
t %>% residuals() %>% ggtsdisplay()
checkresiduals(t,plot = FALSE)
#p-value > 0.05 means significant 

#check AICc
t

#check RMSE
fore = forecast(t,h=24)

tnew=state_raw[(length(state_raw)-51):(length(state_raw)-28)]
tnewnew = t(t(as.vector(fore$mean[1:length(fore$mean)])))

rmse(tnew, tnewnew)
```
# NO.22 Massachusetts
order=c(1,1,2),seasonal=c(0,1,1))AICc=-413.85 RMSE 0.4157668

```{r}
usadata[22,1]
state = c(usadata[22,])
state = state[2:length(state)]
state_raw = as.vector(unlist(state))
ts_state_data=ts(state_raw,start=c(1976, 1), end=c(2018, 12), frequency=12)

# p-value = 0.005 < 0.05
autoresult = auto.arima(ts_state_data,seasonal = TRUE)
checkresiduals(autoresult)#p_v=

#record RMSE
fore = forecast(autoresult,h=24)
tnew=state_raw[(length(state_raw)-51):(length(state_raw)-28)]
tnewnew = t(t(as.vector(fore$mean[1:length(fore$mean)])))

rmse(tnew, tnewnew)#0.55195

# check acf and pacf plot
acf(ts_state_data)
pacf(ts_state_data)
# p-value >0.05 non-stationary
adf.test(ts_state_data)

# difference ts , d = 1
d = diff(ts_state_data, differences=1)
plot.ts(d)

#get p and q from plots
acf(d)
pacf(d)
adf.test(d)
ts_state_data %>% diff(lag=12) %>% diff() %>% ggtsdisplay()

#try orders
t=Arima(ts_state_data,order=c(1,1,2),seasonal=c(0,1,1))
t %>% residuals() %>% ggtsdisplay()
checkresiduals(t,plot = FALSE)
#p-value > 0.05 means significant 

#check AICc
t

#check RMSE
fore = forecast(t,h=24)

tnew=state_raw[(length(state_raw)-51):(length(state_raw)-28)]
tnewnew = t(t(as.vector(fore$mean[1:length(fore$mean)])))

rmse(tnew, tnewnew)
```
# NO.23 Michigan
order=c(2,0,1),seasonal=c(0,1,1))AICc=294.23 RMSE 0.9963709

```{r}
usadata[23,1]
state = c(usadata[23,])
state = state[2:length(state)]
state_raw = as.vector(unlist(state))
ts_state_data=ts(state_raw,start=c(1976, 1), end=c(2018, 12), frequency=12)

# p-value = 0.005 < 0.05
autoresult = auto.arima(ts_state_data,seasonal = TRUE)
checkresiduals(autoresult)#p_v=

#record RMSE
fore = forecast(autoresult,h=24)
tnew=state_raw[(length(state_raw)-51):(length(state_raw)-28)]
tnewnew = t(t(as.vector(fore$mean[1:length(fore$mean)])))

rmse(tnew, tnewnew)#0.55195

# check acf and pacf plot
acf(ts_state_data)
pacf(ts_state_data)
# p-value >0.05 non-stationary
adf.test(ts_state_data)

# difference ts , d = 1
d = diff(ts_state_data, differences=1)
plot.ts(d)

#get p and q from plots
acf(d)
pacf(d)
adf.test(d)
ts_state_data %>% diff(lag=12) %>% diff() %>% ggtsdisplay()

#try orders
t=Arima(ts_state_data,order=c(2,0,1),seasonal=c(0,1,1))
t %>% residuals() %>% ggtsdisplay()
checkresiduals(t,plot = FALSE)
#p-value > 0.05 means significant 

#check AICc
t

#check RMSE
fore = forecast(t,h=24)

tnew=state_raw[(length(state_raw)-51):(length(state_raw)-28)]
tnewnew = t(t(as.vector(fore$mean[1:length(fore$mean)])))

rmse(tnew, tnewnew)
```

# NO.24 Minnesota
order=c(3,0,2),seasonal=c(3,1,1))AICc=-144.05 RMSE 0.6711534

```{r}
usadata[24,1]
state = c(usadata[24,])
state = state[2:length(state)]
state_raw = as.vector(unlist(state))
ts_state_data=ts(state_raw,start=c(1976, 1), end=c(2018, 12), frequency=12)

# p-value = 0.005 < 0.05
autoresult = auto.arima(ts_state_data,seasonal = TRUE)
checkresiduals(autoresult)#p_v=

#record RMSE
fore = forecast(autoresult,h=24)
tnew=state_raw[(length(state_raw)-51):(length(state_raw)-28)]
tnewnew = t(t(as.vector(fore$mean[1:length(fore$mean)])))

rmse(tnew, tnewnew)#0.55195

# check acf and pacf plot
acf(ts_state_data)
pacf(ts_state_data)
# p-value >0.05 non-stationary
adf.test(ts_state_data)

# difference ts , d = 1
d = diff(ts_state_data, differences=1)
plot.ts(d)

#get p and q from plots
acf(d)
pacf(d)
adf.test(d)
ts_state_data %>% diff(lag=12) %>% diff() %>% ggtsdisplay()

#try orders
t=Arima(ts_state_data,order=c(3,0,2),seasonal=c(3,1,1))
t %>% residuals() %>% ggtsdisplay()
checkresiduals(t,plot = FALSE)
#p-value > 0.05 means significant 

#check AICc
t

#check RMSE
fore = forecast(t,h=24)

tnew=state_raw[(length(state_raw)-51):(length(state_raw)-28)]
tnewnew = t(t(as.vector(fore$mean[1:length(fore$mean)])))

rmse(tnew, tnewnew)
```
# NO.25 Mississippi
order=c(3,0,2),seasonal=c(3,1,1))AICc=385.84 RMSE 0.6710053

```{r}
usadata[25,1]
state = c(usadata[25,])
state = state[2:length(state)]
state_raw = as.vector(unlist(state))
ts_state_data=ts(state_raw,start=c(1976, 1), end=c(2018, 12), frequency=12)

# p-value = 0.005 < 0.05
autoresult = auto.arima(ts_state_data,seasonal = TRUE)
checkresiduals(autoresult)#p_v=

#record RMSE
fore = forecast(autoresult,h=24)
tnew=state_raw[(length(state_raw)-51):(length(state_raw)-28)]
tnewnew = t(t(as.vector(fore$mean[1:length(fore$mean)])))

rmse(tnew, tnewnew)#0.55195

# check acf and pacf plot
acf(ts_state_data)
pacf(ts_state_data)
# p-value >0.05 non-stationary
adf.test(ts_state_data)

# difference ts , d = 1
d = diff(ts_state_data, differences=1)
plot.ts(d)

#get p and q from plots
acf(d)
pacf(d)
adf.test(d)
ts_state_data %>% diff(lag=12) %>% diff() %>% ggtsdisplay()

#try orders
t=Arima(ts_state_data,order=c(3,0,2),seasonal=c(3,1,1))
t %>% residuals() %>% ggtsdisplay()
checkresiduals(t,plot = FALSE)
#p-value > 0.05 means significant 

#check AICc
t

#check RMSE
fore = forecast(t,h=24)

tnew=state_raw[(length(state_raw)-51):(length(state_raw)-28)]
tnewnew = t(t(as.vector(fore$mean[1:length(fore$mean)])))

rmse(tnew, tnewnew)
```
# NO.26 Missouri
order=c(3,0,1),seasonal=c(0,1,1))AICc=-49.16 RMSE 0.7054886

```{r}
usadata[26,1]
state = c(usadata[26,])
state = state[2:length(state)]
state_raw = as.vector(unlist(state))
ts_state_data=ts(state_raw,start=c(1976, 1), end=c(2018, 12), frequency=12)

# p-value = 0.005 < 0.05
autoresult = auto.arima(ts_state_data,seasonal = TRUE)
checkresiduals(autoresult)#p_v=

#record RMSE
fore = forecast(autoresult,h=24)
tnew=state_raw[(length(state_raw)-51):(length(state_raw)-28)]
tnewnew = t(t(as.vector(fore$mean[1:length(fore$mean)])))

rmse(tnew, tnewnew)#0.55195

# check acf and pacf plot
acf(ts_state_data)
pacf(ts_state_data)
# p-value >0.05 non-stationary
adf.test(ts_state_data)

# difference ts , d = 1
d = diff(ts_state_data, differences=1)
plot.ts(d)

#get p and q from plots
acf(d)
pacf(d)
adf.test(d)
ts_state_data %>% diff(lag=12) %>% diff() %>% ggtsdisplay()

#try orders
t=Arima(ts_state_data,order=c(3,0,1),seasonal=c(0,1,1))
t %>% residuals() %>% ggtsdisplay()
checkresiduals(t,plot = FALSE)
#p-value > 0.05 means significant 

#check AICc
t

#check RMSE
fore = forecast(t,h=24)

tnew=state_raw[(length(state_raw)-51):(length(state_raw)-28)]
tnewnew = t(t(as.vector(fore$mean[1:length(fore$mean)])))

rmse(tnew, tnewnew)
```